\documentclass[letterpaper, 11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}


\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}


\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%resume->
%Heading
\begin{document}
\begin{center}
    \textbf{\Huge \scshape Ali Alkhulaqi}\\ \vspace {1pt}
    \small 347-750-4280 $|$ href{alialkhulaqi2115@gmail.com} {\underline{alialkhulaqi2115@gmail.com}}$|$
    \href{https://www.linkedin.com/in/ali-alkhulaqi-19a1a3315/} {\underline{linkedin/in/ali-alkhulaqi}}$|$
    \href{https://github.com/AliA749} {\underline{github.com/Ali}}
\end{center}
%Education
\section{Education}
    \resumeSubHeadingListStart
        \resumeSubheading
        {New York Institue of Technology}{Manhattan, NYC}
        {Bachelor of science in Computer Science}{Sep. 2025 -- May 2026}
        \resumeSubheading
        {Queens College}{Flushing, NYC}
        {Bachelor of science in Computer Science}{Aug. 2026 -- May 2029}
    \resumeSubHeadingListEnd
%Experience
\section{Experience}
    \resumeSubHeadingListStart
        \resumeSubheading
        {Coding Coach}{October 2025 -- April 2026}
        {TheCoderSchool}{Bayside, NYC}
            \resumeItemListStart
                \resumeItem{Taught coding fundamentals (Scratch, Python) to 15+ students across skill levels, designing custom lesson
                plans tailored to each learner's pace and goals.}
                \resumeItem{Demonstrated classroom adaptability by substituting across classes, maintaining consistent progress for all
                students.}
                \resumeItem{Introduced project-based learning, guiding advanced students through building functional Python
                applications.}
            \resumeItemListEnd
        \resumeSubheading
        {Backend Developer}{August 2024 -- January 2025}
        {Project Empower}{Remote}
            \resumeItemListStart
                \resumeItem{Architected and implemented user authentication and API routing for a non-profit web platform serving low-
                income, first-generation college students.}
                \resumeItem{Engineered session management logic ensuring zero-error post-login routing across authenticated user
                flows.}
                \resumeItem{Co-organized the Project Empower Hackathon (Jul–Aug 2024) with 2,000+ participants and 200,000 dollars in
                prizes, coordinating logistics and participant communication.}
            \resumeItemListEnd
        \resumeSubheading
        {IT Media Intern}{July 2025 -- August 2025}
        {Skylight Pharmacy}{Jamaica, NYC}
            \resumeItemListStart
                \resumeItem{Produced promotional video content for Instagram and TikTok, growing digital brand engagement.}
                \resumeItem{Launched and managed Google Ads and Meta Ads campaigns, expanding audience reach for the
                pharmacy's digital presence.}
                \resumeItem{Streamlined internal data entry workflows and assisted with day-to-day IT support tasks}
            \resumeItemListEnd
        \resumeSubheading
        {Cashier/Customer Service Lead}{June 2021 -- December 2023}
        {Go Detox}{VanWyck, NYC}
            \resumeItemListStart
                \resumeItem{Led a team of 3, managing daily operations and contributing to a 20–30% sales increase during peak
                summer hours.}
                \resumeItem{Resolved technical issues with third-party delivery platforms (Uber Eats, DoorDash, Grubhub), reducing
                order errors and improving turnaround time under pressure.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd
%Projects
\section{Projects}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {\textbf{Pr-Review-Assistant} $|$ \emph{Typescript, React, Supabase, ClaudeAI, GroqAI}{July 2026 -- Present}}
            \resumeItemListStart
                \resumeItem{Developed a Full-stack web app using Typescript serving the backend and React as the frontend}
                \resumeItem{Implemented Github OAuth to get user's repositories}
                \resumeItem{The AI would look at the chosen pull request and help show vulnerabilities}
                \resumeItem{Used Groq for free AI service while using Claude to help with my planning and implementation}
            \resumeItemListEnd
        \resumeProjectHeading
            {\textbf{Non-Profit Student Database} $|$ \emph{Typescript,MongoDB}{August 2025 -- January 2026}}
            \resumeItemListStart
                \resumeItem{Architected the database schema and secure REST API routes for Project Empower's student-facing
                platform, handling authentication flows and role-based routing logic using Typescript and MongoDB.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd
%programming skills\certs
\section{Technical Skills}
    \begin{itemize}[leftmargin=0.15in,label={}]
        \small{\item{
            \textbf{Languages}{: Java, Python, SQL(MySQL),Rust, Typescript} \\
            \textbf{FrameWorks}{: React, Node.js, Flask, FastAPI} \\ 
            \textbf{Developer Tools}{: Git, Docker, ClaudeAI, Visual Studio Code, IntelliJ, Linux(basics)}\\
            \textbf{Certifcations}{: YouScience(Java Certifcation), Mimo(Typescript Certifcation)}
        }}
    \end{itemize}
\end{document}